---
title: "Lotka-Volterra equations"
author: "Liu, CHIA-HUNG (Eric)"
date: "2021/11/25"
output: html_document
---

# Lotka-Volterra equations
When having two species using the same resources but with different rates of efficiency, we can model their population growth using Lotka-Volterra equations. 
$$ N1_{t+1} = N1_t + \left[ growth.rate \times N1_t \times \left( \frac {K_1-N1_t-\alpha_{12}N2_t} {K_1}\right)\right] $$ 
$$ N2_{t+1} = N2_t + \left[ growth.rate \times N2_t \times \left( \frac {K_2-N2_t-\alpha_{21}N2_t} {K_2}\right)\right] $$
K values are the carrying capacities for each of the two species, both α values are competition coefficients that translate the effect of one species on another. 

### Create a function
The script was wrote by prof. Denis originally. It approached the solution but still not working! So below is the script after I debugged. 

```{r}
grow <- function(start_1, start_2, growth.rate_1 = 3.2, growth.rate_2 = 1.2,
                 K1 = 100, K2 = 120, a12 = 0.8, a21 = 0.8){
  num_gen <- 30
  N1 <- rep(0, 30)
  N2 <- rep(0, 30)
  generation <- rep(1, num_gen)
  N1[1] <- start_1
  N2[1] <- start_2
  for (i in 2:30){
    N1[i] = N1[i-1] + (growth.rate_1 * N1[i-1] * ((K1 - N1[i-1] - a12 * N2[i-1]) / K1))
    N2[i] = N2[i-1] + (growth.rate_2 * N2[i-1] * ((K2 - N2[i-1] - a21 * N1[i-1]) / K2))
    generation[i] = i
  }
if (N1[1] > 0){
  plot(N1 ~ generation, typ="o", ylim=c(0, max(c(K1, K2))), ylab="N",
       sub = paste('N1 = ', start_1, ', N2 = ', start_2))
  legend('right', legend = c('N1', 'N2'), col = c(1, 2), pch = 1, bty = 'n')
} else {
  plot(N1 ~ generation, typ="n", ylim=c(0, max(c(K1,K2))), ylab="N",
       sub = paste('N1 = ', start_1, ', N2 = ', start_2))
}
if (N2[1] > 0){
  lines(N2 ~ generation, typ="o", col = 2)
  legend('right', legend = c('N1', 'N2'), col = c(1, 2), pch = 1, bty = 'n')}
}

```

### Plot a graphic
Plot a graphic to present three different situations.
```{r}
#pdf('Lotka-Volterra equations.pdf', height = 6, width = 4)

par(mar = c(5, 4, 1, 1), mfrow = c(3, 1), las = 1)
grow(1, 0)
text(25, 90, "Species 1 alone")
grow(0, 1)
text(25, 90, "Species 2 alone")
grow(1, 2)
text(25, 90, "Both Species competing")

#dev.off()

```

### Make an animation
The animate can show the change with increasing initial number of the two species. The result would be saved as a gif file.
```{r}
require(animation)
saveGIF({
  for (i in seq(0, 100, 10)) {
    grow(i/2, i, growth.rate_2 = 2)
  }
}, movie.name = 'Species interaction.gif', interval = 0.25)

```

### Show the GIF
To show the GIF in Rmarkdown, we can use the package: gifski
```{r, animation.hook="gifski"}
library(gifski)
for (i in seq(0, 100, 10)) {
    grow(i/2, i, growth.rate_2 = 2)
  }
```
