---
title: "Practice 3"
author: "Liu, CHIA-HUNG (Eric)"
date: "2021/11/22"
output: html_document
---
# Create an interactive map
## Features of my map: introducing instrument shops near NTU. 
### Build up the data base (resource from google map)

```{r}
library(leaflet)
library(tidyverse)
library(sp)
Instr.sp <- data.frame(Name =  c('金螞蟻金山店', '金螞蟻中華店', '金石樂器', '集樂成樂器', '長安樂器'))
Instr.sp$Long <- c(121.5291256640116, 121.51032550667296, 121.53982186840682, 121.51683461233273, 121.52745907906973)
Instr.sp$Lat <- c(25.040298445909055, 25.047794718028047, 25.01517693018381, 25.021866535804904, 25.034273891066)
Instr.sp$Star <- c(4.5, 4.6, 3.3, 5.0, 4.6)
```

### Create a guitar icon to attract users
The picture were uploaded to the website, Imgure, to get the URL of the picture.
```{r}
Guitar <- makeIcon(
  iconUrl = "https://i.imgur.com/4VdEDK6.png",
  iconWidth = 78, iconHeight = 95,
  iconAnchorX = 78, iconAnchorY = 94)
```

### Build the map
Users can know the name of the shops by clicking the icons and knowing costumer judgement by touch the icons.
```{r}
leaflet(Instr.sp) %>%
  addTiles() %>%
  setView(lng = 121.539, lat = 25.030, zoom = 13) %>%
  addProviderTiles(providers$Stamen.TonerLite) %>%
  addMarkers(lng = ~ Long, lat = ~ Lat, icon = Guitar, popup = ~ Name, label = ~ Star)

```
