---
title: "Prctice 2"
author: "Eric Liu"
date: "2021/10/19"
output: html_document
---
# Type the data
## Build a data frame with the weight of each subject

```{r}

before_diet <- c(104, 95, 87, 77, 112)
after_diet <- c(96, 91, 81, 75, 118)
bubble_exp <- data.frame(before_diet, after_diet)
rownames(bubble_exp) <- c('subject_1', 'subject_2', 'subject_3', 'subject_4', 'subject_5')
head(bubble_exp)
str(bubble_exp)

```

# Creat a list `BUBBLE_DIET`
## First element of the list is a data frame defined as `DIET_RESULT`

```{r}

library(tidyr)
DIET_RESULT <- bubble_exp %>%
  pivot_longer(before_diet:after_diet, values_to = 'weight', names_to = 'time')
head(DIET_RESULT, 4)
```

## Second element of the list is a list contained three elements
- First element is a vector of character of the row names of `bubble_exp`

```{r}

subject <- rownames(bubble_exp)

```

- Second element is a numeric vector of the weight loss of each subject (in %)

```{r}
weight_loss <- (bubble_exp$after_diet - bubble_exp$before_diet) / bubble_exp$before_diet * 100

```

- Third element is a data.frame combined the vector `subject` and `weight_loss`

```{r}

subject_weight <- data.frame(subject, weight_loss)
head(subject_weight)
```

- Combined these three elements as a list called `WEIGHT_LOSS`

```{r}

WEIGHT_LOSS <- list(subject = subject, weight_loss = weight_loss, subject_weight = subject_weight )
str(WEIGHT_LOSS)

```

## Finally, combine `DIET_RESULT` and `WEIGHT_LOSS` as a list defined as `BUBBLE_DIET`

```{r}

BUBBLE_DIET <- list(DIET_RESULT = DIET_RESULT, WEIGHT_LOSS = WEIGHT_LOSS)
str(BUBBLE_DIET)

```