---
title: "Practice M1"
author: "Liu, CHIA-HUNG (Eric)"
date: "2021/12/23"
output: html_document
---
Using the tikus data set from the package mvabund. Select observation for the year 1981, 1983, and 1985 only (noted 81, 83 and 85). Build a Bray-Curtis dissimilarity matrix among selected observations. Plot heat map of the respective matrix. Build a network of species co-occurence (presence/absence) based on your selection.

### Import data
Download the package mvabund, choose tikus dataset, and select expected year.
```{r, message=FALSE}
library(cluster)
library(gclus)
library(mvabund)
library(vegan)
library(qgraph)

data("tikus")
str(tikus)
#Split the list into two dataframes
spe.abund <- tikus[[1]]
x <- tikus[[2]]
#Select target year
selected.spe <- spe.abund[x$time == 81 | x$time == 83 | x$time == 85, ]
```

### Build a Bray-Curtis dissimilarity matrix
Use the function `vegdist` to build the Bray-Curtis dissimilarity matrix, and visualize the matrix with the function `coldiss`
```{r, include=FALSE}
#I failed to use the function coldiss in the package gclus. Therefore, I copied its source code from internet. 
coldiss <- function(D, nc = 4, byrank = TRUE, diag = FALSE)
{
  require(gclus)
  
  if (max(D)>1) D <- D/max(D)
  
  if (byrank) {
    spe.color <- dmat.color(1-D, cm.colors(nc))
  }
  else {
    spe.color <- dmat.color(1-D, byrank=FALSE, cm.colors(nc))
  }
  
  spe.o <- order.single(1-D)
  speo.color <- spe.color[spe.o, spe.o]
  
  op <- par(mfrow=c(1,2), pty="s")
  
  if (diag) {
    plotcolors(spe.color, rlabels=attributes(D)$Labels, 
               main="Dissimilarity Matrix", 
               dlabels=attributes(D)$Labels)
    plotcolors(speo.color, rlabels=attributes(D)$Labels[spe.o], 
               main="Ordered Dissimilarity Matrix", 
               dlabels=attributes(D)$Labels[spe.o])
  }
  else {
    plotcolors(spe.color, rlabels=attributes(D)$Labels, 
               main="Dissimilarity Matrix")
    plotcolors(speo.color, rlabels=attributes(D)$Labels[spe.o], 
               main="Ordered Dissimilarity Matrix")
  }
  
  par(op)
}
```

```{r}
#Build matrix
spe.db <- vegdist(selected.spe)
#Draw heatmap
coldiss(spe.db, byrank = F, diag = T)
```


### Build a network of species co-occurence (presence/absence)
Transpose species dataframe, do the presence/absence transformation, and create species co-occurence plot.
```{r}
#transpose species matrix
spe.t <- t(selected.spe)
#P/A transformation, Jaccard dissimilarity matrix
spe.t.eu <- dist(spe.t, 'binary')
#Visualization
qgraph(1-spe.t.eu, layout = 'spring', vsize = 4)
```